---
title: "Untitled"
format: html
editor: visual
---

```{r}
dataCar=read.csv("C:/Users/ReMarkt/Downloads/dataCar.csv")
```

**1.** The dimension of the dataframe `dataCar` (i.e., num. of rows, num. of columns) is: \<`r dim(dataCar)`\>

**2.** The first six lines of this data are

```{r}
library(kableExtra)
#|warning:false
dataCar|>head() |> kableExtra::kbl( booktabs = T,linesep = "")|> 
     kable_styling(latex_options = c("scale_down"))

```

**3.** Using the R function str(), we get the structure of the data

```{r}
str(dataCar)
```

**4.** We made use of the function `subset()` to delete the first column of dataCar and the function `transform()` to transform the variables `clm`, `numclaims`, `veh_body`, `veh_age`, `gender`, `area`, and agecat to factors. Here is the summary of the transformed dataCar

```{r}
#| echo: true
datCar=subset(dataCar,select = -X)
datCar <- datCar |> transform(
  clm = factor(clm),
  numclaims = factor(numclaims),
  veh_body = factor(veh_body),
  veh_age = factor(veh_age),
  gender = factor(gender),
  area = factor(area),
  agecat = factor(agecat)
)
summary(datCar)|> kableExtra::kbl( booktabs = T,linesep = "")|> 
     kable_styling(latex_options = c("scale_down"))

```

**5.** Below is a Barplot of numclaims.

```{r}
#| echo: false
#| fig-cap:
#| 'Barplot of `numclaims`'
tab=table(datCar$numclaims)|> proportions()
barplot(tab)
```
